ZCB Pricing

### 2018-06-24 ZCB Pricing .Rmd
test 2
Testing repository
test 3
test 4
Real Work

---
title: "ZCB Pricing"
author: "VGV"
date: "6/22/2018"
output: html_document
---

@@

```{r}
print("hello world")
```

>>>>

---
title: "ZCB Pricing"
author: 
- Valentine Chisango
- George Parekkadavil
- Vegan Pather

date: "6/22/2018"
output: html_document
---

@@

```{r 1}
# Closed form solution to Bond price

bond_price <- function(alpha,beta,sigma,t,T,r){
  A <- (beta*(1-exp(-beta*(T-t))))/(alpha)
  B <- (1/beta)*((alpha-(sigma)^2/(2*beta))*(A - T +t) - (sigma^(2)*A^2)/(4))
  exp(-A*r +B)
}

```
